---
title: "Alcohol vs Seat choice"
author: "Teresa Juan"
date: "june 2, 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```

## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

The box plot tells us that the back seat drink more alcohol then the front and middle seats. The boxes between the middle and the front seat is about the same, and the back row box is 75 percent bigger then the other two.

## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=davisdata)
```

In the numeric data we can see that the mean for the back seats are 3 times higher the the middle and front seat, showing us that they had more drinks then the other two.

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
Since the P value from one way nova was a very small number, we are going to test and see which categories are different by running a plot TukeyHSD.
```{r}
plot(TukeyHSD(model1))
```

As we run the test we see the middle-back and the front-back seat are in the negative interval line, meaning they had less drinking or about the same alcohol. As we look at the middle-front the interval line is between the negative but more is in the positive numbers meaning they had more drink. this shows us there is a big difference because the interval line goes trough the 0.

## Conclusions

In conclusion the front and middle seat had less alcohol then the back seat, we can tell this by looking at the plot box and prove it by running a TukeyHSD. This test compare the tree categories and came to the conclusion the back seat had a big difference alcohol consumption then the other two.
 
